Benchmarking of Rigetti architecture

### 2023-01-04 txt/maths.tex
maths
maths ended

\begin{equation}
	N_\text{total} = \#\{(\QQ, k, i, j): k = i \}
\end{equation}

@@

The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$,
in terms of their distance with the use of the diamond norm
\begin{equation}
p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond, 
\end{equation}
where 
\begin{equation}
\|\PP\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left(\PP \otimes \1\right) (\proj{\psi}) \|_1.
\end{equation}
The quantum state $\ket{\psi}$ which maximizes the diamond norm is called as discriminator.

Furthermore,  thanks to the proof of the Holevo-Helstrom theorem, it is possible to construct the necessary components  ($\ket{\psi_0}$, $V_0$, $V_1$) to create the optimal discrimination strategy.

@@

So far, we only discussed how the discrimination is performed using two different
schemes, assuming that all needed components ($\ket{\psi_0}$, $V_0$, $V_1$) are known. While the determination of $V_0$ and $V_1$ is a simple task provided the discriminator $\ket{\psi_{0}}$ is known, it turns out, 
sad to say, determining the analytical form of the discriminator $\ket{\psi_{0}}$
is, in general, NP-hard problem. 
We have found the analytical solution of the discrimination scheme for a particular class of von Neumann measurements.

@@

\begin{equation}
	U = H
	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger, 
\end{equation}
where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.

\begin{theorem}
The optimal probability of correct discrimination between von Neumann
measurements $\PP_U$ and $\PP_{\Id}$ is given by
\begin{equation}
p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
\end{equation}
\end{theorem}

\begin{proposition}\label{prop-discrim}
 The optimal input state has the form
\begin{equation}
\ket{\psi_{0}} = \frac{1}{\sqrt{2}} |\Id_2 \rangle \rangle.
\end{equation}
\end{proposition}

\begin{proposition}
The  optimal measurement has the following form
\begin{equation}
\begin{split}
\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1
\proj{0} V_1^\dagger,   \\
\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1
\proj{1} V_1^\dagger,
\end{split}
\end{equation}
where for each $\phi \in \mathbb{R}$ and  the unitaries $V_0$,  $V_1$
have the following form
\begin{equation}
V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
\end{equation}
\begin{equation}
V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right)
&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
\end{equation}
\end{proposition}

>>>>

\begin{equation}
	N_\text{total} = \#\{(\QQ, k, i, j): k = i \}. 
\end{equation}

@@

The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum measurements, $\PP$  and $\mathcal{Q}$,
in terms of their distance with the use of the diamond norm
\begin{equation}
p_{\text{succ}}(\PP, \mathcal{Q}) =  \frac12 + \frac14 \| \PP - \mathcal{Q} \|_\diamond, 
\end{equation}
where 
\begin{equation}
\|\PP\|_\diamond = \max_{\| \ket{\psi}\|_1=1} \| \left(\PP \otimes \1\right) (\proj{\psi}) \|_1.
\end{equation}
The quantum state $\ket{\psi}$ which maximizes the diamond norm is called as discriminator.
Furthermore,  thanks to the proof of the Holevo-Helstrom theorem, it is possible to construct the necessary components  ($\ket{\psi_0}$, $V_0$, $V_1$) to create the optimal discrimination strategy.

@@

So far, we only discussed how the discrimination is performed using two different
schemes, assuming that all needed components ($\ket{\psi_0}$, $V_0$, $V_1$) are known. It turned out that the determination of $V_0$ and $V_1$ is a simple task while the discriminator $\ket{\psi_{0}}$ is known. However, 
sad to say, determining the analytical form of the discriminator $\ket{\psi_{0}}$
is, in general, NP-hard problem. 
We have found the analytical solution of the discrimination scheme for a particular class of von Neumann measurements.

@@

\begin{equation}
	U = H
	\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger, 
\end{equation}
where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
In this case, the optimal input state is Bell state of the form
\begin{equation}
\ket{\psi_{0}} = \frac{1}{\sqrt{2}} \ket{00} + \ket{11}.
\end{equation}
And, for a given angle  $\phi \in  [0, 2 \pi)$,   the unitaries $V_0$,  $V_1$
have the following form
\begin{equation}
V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i
\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi -
\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
\end{equation}
\begin{equation}
V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i
\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right)
&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
\end{equation}
Finally, we have also calculated the theoretical probability of correct discrimination between von Neumann
measurements $\PP_U$ and $\PP_{\Id}$ is given by
\begin{equation}
	p_{\text{succ}}(\PP_{U}, \PP_{\Id}) = \frac{1}{2} + \frac{|1 - e^{i \phi}  |}{4} .
\end{equation}
More details and proofs of the construction's validity   we can find in the article \cite{}.
